The 2014 SMT Competition

### 2015-08-03 2014/report/SMTCOMP.tex
Whitespace.
Non-existing reference replaced.

The SAT decision problem can be generalized by replacing
Boolean variables with atomic predicates built with symbols from a
background theory, or a combination of background theories. The
resulting decision problem is called \emph{Satisfiability Modulo
  Theories\/} ~\cite{DBLP:conf/jelia/Tinelli02}. The background theories of interest arise from
	application domains, such as formal verification or scheduling problems, and include arrays,
bit-vectors, equality with uninterpreted functions, linear and
non-linear arithmetics over integers and real numbers. Also, a theory
may explicitly allow or disallow quantification. Tools addressing the
SMT problem are called \emph{SMT solvers\/}. An SMT solver is often
built by combining a SAT solver with (semi-)decision procedures for
specific theories.

@@

Competitions among tools for a specific purpose are now common. Indeed SMT-COMP participated among dozen or so tools in the
FLoC Olympic Games in 2014~\cite{TBD}. The competitions differ, of course, in their target problem set, but also differ in
their overall goals, scoring policies, and organization.

>>>>

The SAT decision problem can be generalized by replacing
Boolean variables with atomic predicates built with symbols from a
background theory, or a combination of background theories. The
resulting decision problem is called \emph{Satisfiability Modulo
  Theories}~\cite{DBLP:conf/jelia/Tinelli02}. The background theories of interest arise from
	application domains, such as formal verification or scheduling problems, and include arrays,
bit-vectors, equality with uninterpreted functions, linear and
non-linear arithmetics over integers and real numbers. Also, a theory
may explicitly allow or disallow quantification. Tools addressing the
SMT problem are called \emph{SMT solvers\/}. An SMT solver is often
built by combining a SAT solver with (semi-)decision procedures for
specific theories.

@@

Competitions among tools for a specific purpose are now common. Indeed SMT-COMP participated among dozen or so tools in the
FLoC Olympic Games in 2014~\cite{FLoC2014}. The competitions differ, of course, in their target problem set, but also differ in
their overall goals, scoring policies, and organization.
